Feasibility Study for the Final State $hh\rightarrow (b\bar{b})(b\bar{b})$

### 2015-05-31 doc/HH4b_Documentation.tex
Updated documentation

@@

The resolved selection requires the presence of at least four b-tagged anti-$k_T$ $R=0.4$ jets with $p_T >$25~GeV and $|\eta|>2.5$.
\textit{Pre-cut} histograms are written out for various kinematic distributions for all events with at least four b-tagged jets but before applying
further kinematic cuts. \textit{Post-cut} histograms contain only events where the four jets also pass the above kinematic cuts.

@@

>>>>

\subsection{Object Definition and Selection}

All jets are clustered using all final state particles after the parton shower (but before hadronisation) as input.

Small-$R$ jets are anti-$k_T$ $R=0.4$ jets. They are required to have $p_T > 40$~GeV and $|\eta|<2.5$.

Small-$R$ subjets are anti-$k_T$ $R=0.3$ jets. They are required to have $p_T > 50$~GeV and $|\eta|<2.5$.

Large-$R$ jets are anti-$k_T$ $R = 1.0$ jets with $p_T > 200$~GeV and $|\eta|<2.0$ (the smaller pseudorapidity is an experimental requirement related to the trackjet-based calibration). They are also required to be mass-drop tagged using the FastJet default parameters: $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$.

Small-$R$ jets are $b$-tagged as follows: True $b$-jets, which have at least one $b$-quark among their constituents, have a 80\% $b$-tagging probability. For all other jets, a mistag rate of 0.01 is used.

Large-$R$ jets are $b$-tagged by ghost-associating anti-$k_T$ $R=0.3$ (selected as above) to the large-$R$ jets. A large-$R$ jets is considered $bb$-tagged if the leading and subleading $p_T$ associated subjets are $b$-tagged.

@@

The resolved selection requires the presence of at least four $b$-tagged, selected anti-$k_T$ $R=0.4$ jets.

@@

\subsection{Boosted Topology}

The boosted selection requires the presence of at least two $bb$-tagged, selected anti-$k_T$ $R=1.0$ jets which are taken as the two Higgs boson candidates.

\subsection{Intermediate Topology}

The intermediate topology requires the presence of at least one $bb$-tagged, selected anti-$k_T$ $R = 1.0$ jet. If there is more than one, the leading one is taken as the first Higgs boson candidate. In addition, there must be at least two anti-$k_T$ $R=0.4$ jets with a separation $\Delta R > 1.0$ with respect to the large-$R$ jet
that is selected as a Higgs boson candidate. The second Higgs boson candidate is reconstructed from the two small-$R$ jets that minimise the difference $|m_{fj} - m_{j1j2}|$.

\subsection{Higgs Mass Window Cut}

All Higgs candidates are required to meet the following Higgs mass window cut: $|m_{H} - 125| < 40$~GeV

[THE INFORMATION BELOW HAS NOT BEEN UPDATED YET]
